Analyzing the impact of social attributes on commit integration success

### 2017-02-21 Paper/MSRChallenge2017.tex
addressed more related work todos

In particular, we analyzed contributions in the 
context of continuous integration, using the technical factors found in
some\todo{First: don't use the word some basically ever.  Second: I'm not sure
  what it means to analyze technical factors found in social attributes.  Maybe rephrase?} of the social attributes provided in the challenge
corpus~\cite{msr17challenge}, and the social factors found on a developer's
GitHub profile.  We used the technical factors to estimate the complexity of the
commit, and the social factors to estimate the developer's experience.
Overall, our study investigates how well different technical and social factors predict
contribution quality. This information can help core team members prioritize project
contributions, and will also provide a further understand of quality enforcement
in the software development process.

>>>>

In particular, we analyzed contributions in the 
context of continuous integration, using the technical factors and one social
factor found in the challenge
corpus~\cite{msr17challenge}, and the social factors found on a developer's
GitHub profile.  We used the technical factors to estimate the complexity of the
commit, and the social factors to estimate the developer's experience.
Overall, our study investigates how well different technical and social factors predict
contribution quality. This information can help core team members prioritize project
contributions, and will also provide a further understand of quality enforcement
in the software development process.
